---
title: "lab_7_multiple_linear_regression_intro"
author: "Lauren Harris"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Explore penguins

Use `GGally::ggpairs()` to create a pairs plot (pairwise comparisons of any two variables)
```{r}
ggpairs(penguins)
```

That's kind of overkill, let's simplify the variables that we include in our ggpairs plot

- species
- bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

## Multiple linear regression

Trying to understand the relationships between multiple predictor variables and an outcome variable which is penguin body mass

The different predictor variables we will try  are:
- species
- flipper length
- sex
- bill depth

### Model 1

Model body mass based only on flipper length and bill depth (bad idea...there are important variables missing)
```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# call a model by name to return only coefficients
model_1

# more info on coefficients in model, use summary
summary(model_1)
```

If everything else is held constant, we expect that for each 1 mm increase in flipper length, penguin body mass is expected to increase by 51.54 g, on average

76.1% of the variance in body mass is explained by flipper length and bill depth

Actually, we think that a model for penguin body mass should contain the variables species, flipper length, and penguin sex

```{r}
model_2 <- lm(body_mass_g ~ species + flipper_length_mm + sex, data = penguins)

# let's check out coefficients
model_2
summary(model_2)
```

Reference level was set as a female Adelie

Interpreting coefficients for flipper length, Gentoo and male

- if all else is held constant, then we expect that for every 1 mm increase in flipper length, we expect a 20.02 g increase in body mass

- If all else is held constant, then we expect that on average a Gentoo penguin will be 836.26 g heavier than an Adelie penguin

- If all else is held equal, then we expect that on average a male penguin will be 530.38 g heavier than a female penguin

## Visualize this model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~sex)
```

## A couple ways to get and report MLR model outcomes

Use     broom::tidy()` to get model coefficient info in a tidy data frame

```{r}
penguin_model_2_coef <- tidy(model_2)

penguin_model_2_coef
```

Try to write in-line code that spits out the coefficient for Gentoo

`r penguin_model_2_coef$estimate[3]` which is not quite as good as `r penguin_model_2_coef[penguin_model_2_coef$term == "speciesGentoo", ]$estimate`

## Look at model diagnostics

Use `plot()` function

```{r}
plot(model_2)
```

## Report the model outputs in a summary table

```{r}
modelsummary(model_2)
```

Use stargazer
```{r, results = "asis"}
stargazer(model_2, type = "html")
```

